Using Git to Manage CogX KTH Code

### 2009-09-21 kth/trunk/doc/cogx-kth-git/source/cogx-kth-git.tex
Docs for svn/git maintenance (KTH only)

\subsection{Feature Development}
\begin{itemize}
  \item Checkout the master branch:
    \begin{lstlisting}
git checkout master
    \end{lstlisting}
  \item Pull updates from the central server and merge them to master:
    \begin{lstlisting}
git pull
    \end{lstlisting}
  \item Create and checkout a topic branch for the new feature:
    \begin{lstlisting}
git checkout -b topic
    \end{lstlisting}
  \item Do some work in the topic branch:
    \begin{lstlisting}
echo "contents" > file
git add file
git commit -m "First commit"
echo "contents2" > file2
git add file2
git commit -m "Second commit"
    \end{lstlisting}
  \item Merge with the master branch:
    \begin{lstlisting}
git checkout master
git merge --squash topic
git commit
    \end{lstlisting}
  \item Push the changes upstream:
    \begin{lstlisting}
git push
    \end{lstlisting}
  \item Do more work in the topic branch:
    \begin{lstlisting}
git checkout topic
echo "new contents" > file
git add file
git commit -m "Third commit"
    \end{lstlisting}
  \item Pull some new updates from the central server and merge them to master:
    \begin{lstlisting}
git checkout master
git pull
    \end{lstlisting}
  \item Rebase the topic branch against the new changes:
    \begin{lstlisting}
git checkout topic
git rebase master
    \end{lstlisting}
  \item Merge the changes with the master branch:
    \begin{lstlisting}
git checkout master
git merge --squash topic
git commit
    \end{lstlisting}
  \item Push the changes upstream:
    \begin{lstlisting}
git push
    \end{lstlisting}

@@

\subsection{Pulling Changes from SVN}
\hl{Missing}

\end{itemize}

>>>>

\subsection{Feature Development}
\begin{itemize}
  \item Checkout the master branch:
    \begin{lstlisting}
git checkout master
    \end{lstlisting}
  \item Pull updates from the central server and merge them to master:
    \begin{lstlisting}
git pull
    \end{lstlisting}
  \item Create and checkout a topic branch for the new feature:
    \begin{lstlisting}
git checkout -b topic
    \end{lstlisting}
  \item Do some work in the topic branch:
    \begin{lstlisting}
echo "contents" > file
git add file
git commit -m "First commit"
echo "contents2" > file2
git add file2
git commit -m "Second commit"
    \end{lstlisting}
  \item Merge with the master branch:
    \begin{lstlisting}
git checkout master
git merge --squash topic
git commit
    \end{lstlisting}
  \item Push the changes upstream:
    \begin{lstlisting}
git push
    \end{lstlisting}
  \item Do more work in the topic branch:
    \begin{lstlisting}
git checkout topic
echo "new contents" > file
git add file
git commit -m "Third commit"
    \end{lstlisting}
  \item Pull some new updates from the central server and merge them to master:
    \begin{lstlisting}
git checkout master
git pull
    \end{lstlisting}
  \item Rebase the topic branch against the new changes:
    \begin{lstlisting}
git checkout topic
git rebase master
    \end{lstlisting}
  \item Merge the changes with the master branch:
    \begin{lstlisting}
git checkout master
git merge --squash topic
git commit
    \end{lstlisting}
  \item Push the changes upstream:
    \begin{lstlisting}
git push
    \end{lstlisting}
\end{itemize}

@@

\subsection{Pulling Changes from SVN}
Setup a joint GIT/SVN local repository:
\begin{itemize}
\item setup another local repository for instance by making a copy of your current 
git repository: cp -r my\_git\_repo svn-git\_repo
\item enter the directory with the repository: cd svn-git\_repo
\item checkout branch master: git checkout master
\item remove all files apart from the .git directory
\item run svn co https://codex.cs.bham.ac.uk/svn/nah/cogx/code/kth/trunk
\item move all the files from trunk to your git working copy: mv trunk/* .
\end{itemize}

Now you have a joint git/svn working copy. To pull new changes from svn and 
merge them to git, do as follows:
\begin{itemize}
\item if you messed up sth with the files, you can do git reset --hard
\item now, pull the most recent version of the master branch: git pull
\item update the changes from the SVN: svn up
\item commit the changes to git: git add/git commit
\item push the changes to the shared repository: git push
\end{itemize}
